---
title: "delphyR – synthetic study report"
lang: en
format:
  html:
    html-table-processing: none
    embed-resources: true
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: false
execute:
  echo: false
  warning: false
  message: false
  error: false
---

```{r}
# Only this packaged template is executable. All study content remains JSON data.
x <- jsonlite::fromJSON("report-data.json", simplifyVector = TRUE)
# Study text is written as character entities inside raw HTML blocks. No
# markup, Markdown link or image, shortcode or code in a study text is
# interpreted, and a text can never end the block that contains it.
escape <- function(value) {
  value <- as.character(value)
  value[is.na(value)] <- "not available"
  rules <- list(c("&", "&amp;"), c("<", "&lt;"), c(">", "&gt;"), c('"', "&quot;"), c("'", "&#39;"), c("`", "&#96;"), c("{", "&#123;"), c("}", "&#125;"))
  for (rule in rules) value <- gsub(rule[1], rule[2], value, fixed = TRUE)
  value
}
raw_html <- function(...) cat("\n```{=html}\n", ..., "\n```\n", sep = "")
cell <- function(column) if (is.list(column)) vapply(column, function(v) paste(as.character(unlist(v)), collapse = "; "), character(1)) else column
show_table <- function(table, empty = "No entries.") {
  if (!is.data.frame(table) || !nrow(table)) {
    raw_html("<p>", escape(empty), "</p>")
    return(invisible(NULL))
  }
  rows <- do.call(paste0, lapply(table, function(column) paste0("<td>", escape(cell(column)), "</td>")))
  raw_html(
    '<div style="overflow-x:auto"><table class="table table-sm table-striped" data-quarto-disable-processing="true"><thead><tr>',
    paste0('<th scope="col">', escape(names(table)), "</th>", collapse = ""), "</tr></thead><tbody>\n",
    paste0("<tr>", rows, "</tr>", collapse = "\n"), "\n</tbody></table></div>"
  )
}
show_json <- function(value) raw_html("<pre>", escape(jsonlite::toJSON(value, auto_unbox = TRUE, pretty = TRUE, null = "null", na = "null")), "</pre>")
show_lines <- function(value) raw_html(paste0("<p>", escape(as.character(unlist(value))), "</p>", collapse = "\n"))
```

# Purpose, design and data scope

This report contains synthetic development data. It is not a public data
release and not a scientific or institutional study approval. Example
thresholds are not methodological recommendations. Agreement among panel
members is not evidence of truth or effectiveness; dissent and insufficient
data are legitimate results.

```{r}
#| results: asis
show_json(x$metadata)
```

# Protocol, rules and amendments

Valid numeric ratings form the denominator. Abstention and inability to judge
are not zero ratings. Quartiles use type 7. Consensus classification, change
between rounds and human item decisions are presented separately.

```{r}
#| results: asis
show_json(x$protocol)
show_table(x$protocol_versions)
```

# Recruitment and participation

Counts refer to the time of export. "consent_recorded" counts members with a
recorded consent to the study information of that round.

```{r}
#| results: asis
show_table(x$recruitment)
show_table(x$rounds)
show_table(x$participation, "No round has enrolled panel members yet.")
```

# Instruments

The texts and versions are those of each conducted round. They are not
individual responses.

```{r}
#| results: asis
show_table(x$instrument)
```

# Results by round

```{r}
#| results: asis
show_table(x$results, "No round has been frozen and analysed yet.")
show_table(x$denominators, "Denominators are not part of this profile or no round is frozen.")
show_table(x$missingness, "Missingness is not part of this profile or no round is frozen.")
show_table(x$distributions, "No distributions in this profile.")
```

# Change between rounds

Paired statistics describe panel members with valid ratings in both rounds.
Attrition is reported separately. A changed item version is compared only where
the study team recorded an explicit comparability decision; otherwise it is
shown as not comparable. Unchanged ratings can express stable dissent.

```{r}
#| results: asis
show_table(x$comparisons, "Fewer than two frozen rounds; no comparison.")
show_table(x$comparability, "No comparability decision recorded.")
```

# Feedback provided

Each released feedback is an immutable artifact identified by its hash. A
corrected feedback is a further artifact; "replaced_by" names the version that
later views received instead.

```{r}
#| results: asis
show_table(x$feedback, "No feedback has been released.")
```

# Qualitative work, item decisions and lineage

These records reflect the state at export time. Qualitative originals and
account mappings are never part of a report.

```{r}
#| results: asis
show_table(x$qualitative)
show_table(x$decisions, "No item decision recorded.")
show_table(x$lineage, "No item split or merge recorded.")
```

# Final items, persistent dissent and undecided items

The classification is the rule outcome of the last frozen round. The
disposition is the study team's own decision; "not documented" means that no
decision was recorded for that round.

```{r}
#| results: asis
show_table(x$final_items, "No frozen round.")
```

# Author-supplied documentation

The software does not invent authorship, funding, conflicts of interest,
approvals, interpretation or deviations. Statements below were entered by the
study team; a recorded reference to an approval does not grant one. This table
is not an ACCORD or CREDES certification.

```{r}
#| results: asis
show_table(x$documentation)
```

# Data dictionary

```{r}
#| results: asis
show_table(x$dictionary)
```

# Reproduction and limitations

Scientific hashes link each snapshot, its rules and its analysis. The report
timestamp changes on re-export; HTML bytes do not replace comparison of
canonical analysis results.

```{r}
#| results: asis
show_lines(x$limitations)
show_json(x$provenance)
raw_html("<p>Report data hash: <code>", escape(x$content_hash), "</code></p>")
```

Pseudonyms are not anonymous. Report release, methodological assessment and
further disclosure remain human decisions.
