---
title: "delphyR – synthetic study report"
lang: en
format:
  html:
    embed-resources: true
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: false
execute:
  echo: false
  warning: false
  message: false
  error: false
---

```{r}
# Only this packaged template is executable. All study content remains JSON data.
x <- jsonlite::fromJSON("report-data.json", simplifyVector = TRUE)
escape <- function(value) {
  value <- as.character(value)
  value[is.na(value)] <- "not available"
  value <- gsub("&", "&amp;", value, fixed = TRUE)
  value <- gsub("<", "&lt;", value, fixed = TRUE)
  value <- gsub(">", "&gt;", value, fixed = TRUE)
  value <- gsub('"', "&quot;", value, fixed = TRUE)
  gsub("'", "&#39;", value, fixed = TRUE)
}
show_table <- function(table) {
  if (!is.data.frame(table) || !nrow(table)) {
    cat("<p>Not documented or no entries in the approved profile.</p>\n")
    return(invisible(NULL))
  }
  cat('<div style="overflow-x:auto"><table><thead><tr>',
      paste0("<th scope=\"col\">", escape(names(table)), "</th>", collapse = ""),
      "</tr></thead><tbody>")
  for (i in seq_len(nrow(table))) cat("<tr>", paste0("<td>", escape(unlist(table[i, ], use.names = FALSE)), "</td>", collapse = ""), "</tr>")
  cat("</tbody></table></div>\n")
}
show_json <- function(value) cat("<pre>", escape(jsonlite::toJSON(value, auto_unbox = TRUE, pretty = TRUE, null = "null", na = "null")), "</pre>\n")
```

# Purpose and data scope

This report contains synthetic development data. It is not a public data release
or scientific or institutional study approval. Example thresholds are not
methodological recommendations.

```{r}
#| results: asis
show_json(x$metadata)
```

# Protocol and rules

Valid numeric ratings form the denominator. Abstention and inability to judge
are not zero ratings. Quartiles use type 7. Consensus classification and human
item decisions are presented separately.

```{r}
#| results: asis
show_json(x$protocol)
```

# Frozen instrument

The following texts and versions come from the instrument used in the analysed
round. They are not individual responses.

```{r}
#| results: asis
show_table(x$instrument)
```

# Results and denominators

```{r}
#| results: asis
show_table(x$results)
show_table(x$denominators)
```

# Missingness and distributions

```{r}
#| results: asis
show_table(x$missingness)
show_table(x$distributions)
```

# Editorial decisions and item lineage

These structured records reflect the state at export time. They do not become
part of the earlier frozen response snapshot. Qualitative originals, free-text
editorial rationales and account mappings are excluded.

```{r}
#| results: asis
show_table(x$decisions)
show_table(x$lineage)
```

# Author information still required

The software does not invent scientific interpretation, funding, conflicts of
interest or missing approvals. The following table is not ACCORD/CREDES certification.

```{r}
#| results: asis
show_table(x$author_fields)
```

# Data dictionary

```{r}
#| results: asis
show_table(x$dictionary)
```

# Reproduction and limitations

Scientific hashes link the snapshot, rules and analysis. The report timestamp
may change on re-export. HTML bytes do not replace comparison of canonical
analysis results.

```{r}
#| results: asis
show_json(x$provenance)
cat("<p>Report data hash: <code>", escape(x$content_hash), "</code></p>")
```

The research export profile contains no contacts or access tokens. Pseudonyms
are not anonymous. Report release, methodological assessment and further
disclosure remain human decisions.
