---
title: "A synthetic panel workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A synthetic panel workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`delphyrApp` separates the panel's response form from the transactional
`delphyr` services. This vignette describes the synthetic development path;
production authentication and deployment are not qualified.

## Start with a trusted identity

An application host creates the repository connection and resolves the actor
on the server. Neither a role selector nor a URL parameter may establish an
identity. A local demonstration starts with an existing synthetic actor:

```{r launch, eval=FALSE}
app <- delphyrApp::run_app(repo, actor, language = "en")
shiny::runApp(app, host = "127.0.0.1")
```

The application does not close the repository connection: its owner manages
connection lifetime. A multi-user host must provide the correct trusted actor
for each session; sharing one demo actor is not authentication.

## Read, respond, review

Choose a study, select a round, and load its questionnaire. Study information is
shown as stored, including its language. Record consent explicitly. Each
response field starts without a preselected rating. A response may instead use
one of the missing-response categories allowed by that study's scale.

Save each response field. The status changes to **Saved** only after a service
returns a committed revision and timestamp. Failed saves retain the pending
form value. A conflict requires reloading and reviewing the authoritative
version; automatic overwriting is not offered.

The progress count means confirmed response fields, rather than question
pages or participants. Save pending changes before submitting. The final
confirmation is intentional: the core service forbids editing after submission.
Required fields, round state, deadline, consent, ownership, and revision-set
consistency are checked again by the core service. A successful submission
returns its receipt and server timestamp.

## Management

A server-authorized manager can view round status and request a lifecycle
transition with a reason and explicit confirmation. The service repeats
permission checks and verifies the instrument hash. A hidden control is never
the authorization boundary. A closed round can be frozen, then analysis and
export jobs can be queued for a separate trusted worker. Check the operation
to retrieve results. Review the exact feedback candidate before release and
assign it to an unopened subsequent round. Bilingual CSV instruments are
validated and previewed before round preparation. Export downloads recheck
permissions.

## Current scope

The P0 interface offers bilingual navigation, labeled controls, keyboard focus,
responsive forms, and live save-status regions. It does not claim formal
accessibility conformance. Autosave, production login, real mail, full editing modules, and cross-browser acceptance remain
separate work. Service injection supports deterministic module testing without
a live database.
