---
title: "Running and reviewing a synthetic Delphi study"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running and reviewing a synthetic Delphi study}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`delphyrApp` separates the study interface from the transactional services in
`delphyr`. This guide covers synthetic development workflows. Production
identity infrastructure and deployment remain separate acceptance gates.
Interface languages are English, German, and French; English is the initial
default. Stored study and instrument texts keep their explicitly authored
language and are not automatically translated.

## Start a trusted local session

For a local instance with one fixed synthetic identity:

```{r launch, eval=FALSE}
# repo and actor come from trusted server-side demonstration setup.
app <- delphyrApp::run_app(repo, actor, language = "en")
shiny::runApp(app, host = "127.0.0.1")
```

The caller owns the lifetime of a directly supplied connection. All sessions of
this instance use the same fixed actor; this is not a multi-user login. Never
resolve identity or roles from browser fields or URL parameters.

A trusted host can instead supply a connection and identity resolver for each
session. This example shows the contract; its deliberate error marks the
host-specific identity adapter that still needs to be supplied:

```{r session-factories, eval=FALSE}
make_repository <- function() {
  delphyr::connect_repository(
    host = "127.0.0.1", port = 55439, dbname = "delphyr",
    user = "delphyr_runtime", environment = "development"
  )
}
resolve_actor <- function(session, repo) {
  stop("Configure a verified server-side identity adapter before use")
}
app <- delphyrApp::run_app(
  repo_factory = make_repository,
  actor_factory = resolve_actor,
  language = "en"
)
```

Factory-created connections close when their session ends. Failed identity
resolution ends the session before service access. The factory contract does
not by itself qualify an OIDC gateway. Local gateway evidence and the remaining
stock Shiny Server OSS transport limitations are documented separately.

## Read, respond, and submit

Choose a study and an assigned round, load the questionnaire, and read the
stored study information. Record consent explicitly. Ratings have no
preselected midpoint. A field can instead use a special response category
permitted by its scale.

Save each response explicitly. **Saved** appears only after a committed revision
and server timestamp return. A failed save preserves the pending form value.
For a revision conflict, reload and review the authoritative server state;
automatic overwriting is not offered.

The progress count means confirmed response fields. Save pending changes before
confirming final submission. The service checks consent, ownership, rights,
deadline, required fields, and the exact revision set again. A successful
submission returns a durable receipt and ends editing for that round.

During connection loss, the interface must not imply that changes are saved.
The tested disconnect/reload path restores the last committed value. It does
not provide an offline editor or preserve unsaved text in browser storage.

## Review rounds, feedback, and reports

Managers inspect the instrument and round state. A transition needs a reason
and confirmation; the service rechecks the instrument hash and authority.
Freeze a closed round before queuing analysis. A separate worker processes
analysis and export jobs. Use **Check operation** to refresh their status.

Preview the exact feedback candidate before approving release. Released
feedback can be assigned to an unopened next round. The panel sees approved
aggregates and its own prior answers, with changed-wording notices where
applicable. Bilingual instrument CSVs are validated and previewed before round
preparation; interface language support does not create missing translations.

Managers can also inspect immutable protocol versions, upload a complete
replacement JSON protocol, review field changes, and explicitly approve an
amendment for future rounds. Existing rounds retain their original protocol.
This is technical versioning, not an institutional or ethical approval.

Downloads recheck authority and integrity. The numeric research profile
contains the snapshot, protocol, results, provenance, dictionary, instrument
texts, and an HTML report. The worker uses a trusted Quarto template when its
optional runtime is available. Otherwise a basic HTML fallback is labelled;
a real render failure remains a failed job. Qualitative originals and individual
free-text answers are excluded. Missing author information is not invented.

## Preserve sources and review editorial work

Editors keep synthetic originals and create separate redactions or summaries
with a reason. Summaries are labelled as summaries, not quotations. Another
authorized person reviews the exact version before release.

Theme versions, inclusion/exclusion coding, source links, and item splits or
merges preserve their provenance. Linking a source does not import an instrument
item. Hidden interface sections never replace service-level authorization.

## Import contacts without granting access

Coordinators can preview synthetic UTF-8 contact CSVs and inspect blocking
row/column issues. Duplicate references, duplicate addresses, and ambiguous
local-part case variants require correction and a new preview. Normal trailing
LF or CRLF file terminators are supported without changing the uploaded hash.

Explicit approval imports the whole reviewed file atomically and returns a
receipt for unbound invitation drafts. It creates no account, consent, response
link, or round enrollment. Separate invitation services require approval of an
existing stable issuer/subject identity; the complete invitation browser journey
is not established by this CSV workflow.

## Approve synthetic campaigns

Coordinators choose exact study pseudonyms and final message text. The resulting
preview binds both content and recipients. A change requires a new preview;
release needs explicit confirmation and a reason.

A separate worker writes only local test receipts. It rechecks participation,
rights, withdrawal, and—for reminders—whether submission already occurred.
The interface sends no email. Cancellation stops remaining processing without
deleting existing receipts. An expired in-flight lease becomes
`delivery_unknown` and is not blindly retried.

## Design and remaining qualification

The interface uses system fonts, visible labels, keyboard focus, responsive
forms, and live status regions. Language changes must preserve pending values;
color alone does not communicate status. Permission-filtered navigation retains
open forms when moving between study sections.

These are design choices and specific local checks, not formal accessibility
certification. Assistive technologies, the complete cross-browser matrix,
autosave, production login, external mail, and operational approval remain
separate gates. Service injection supports focused module tests without a
database; those tests do not replace actual PostgreSQL and browser evidence.
